Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex
bookmark

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
\newcommand{\OpDistance}{\mathbfcal{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\Mask}{\bm{M}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

\subsection{Unknowns and Prior Knowledge}
\label{sec:prior}

In general terms, the variables are the set
\begin{equation}
  {\cal V}\equiv
  \left\{
    {\bm n},
    \left\{
      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm g}_{\lambda}
    \right\}_{\lambda}
  \right\}
  \;\;,
  \label{eq:calV}
\end{equation}
where $\lambda$ denotes the spectral (color) channel.  There are
$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
    spectral})$}.

\subsection{Objective Function}
\label{sec:objective-function}

@@

>>>>

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
\newcommand{\OpDistance}{\mathbfcal{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\Mask}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

@@

In general terms, the variables are the set \mbox{$\left\{{\bm
      n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
        g}_{\lambda}\right\}_{\lambda}\right\}$} where $\lambda$
denotes the spectral (color) channel.  There are $N_{\rm spectral}$
spectral channels.  Thus, the number of unknown variables is in
principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm spectral})$}.
